---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```


```{css}
@import url('https://fonts.googleapis.com/css2?family=Cinzel:wght@400..900&display=swap');

h2 {
  font-family: 'Cinzel', serif;
  font-weight: 900; color: #8686AC
}
```


```{css}
@import url('https://fonts.googleapis.com/css2?family=Changa:wght@200..800&family=Cinzel:wght@400..900&display=swap');

p {
  font-family: 'Changa', sans-serif
}
```


## The daily number of emails received in two email addresses, considering the categories of the emails.

This analysis aims to compare the number and types of emails received by personal and school addresses, identifying any noticeable differences in email frequency and category distribution over time.

<br>

```{r}
library(tidyverse)

csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSonJKLDS4YZ9bn-cacFyUGhOlDFZguHG8ESZ5pHg8a2FQ_WhIDKdnUEb4t-GvpbiLO-oZDJAdJBxei/pub?gid=150202961&single=true&output=csv"

logged_data <- read_csv (csv_file)

latest_data <- logged_data %>%

 rename(date_of_emails = 2, total_emails = 3, major_emails =4, more_email_address= 5, first_email_time= 6, first_email_type= 7, last_email_time= 8, last_email_type= 9, rating_scale= 10)

daily_max <- max(latest_data$total_emails)

daily_min <- min(latest_data$total_emails)

daily_mean <- round(mean(latest_data$total_emails),2)

```

The daily maximum number of emails is `r daily_max`.

The daily minimum number of emails is `r daily_min`.

The daily mean number of emails is `r daily_mean`.

<br>

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = major_emails), fill=c("#4A4A4A","#CBCBC0","#FFFFE3","#6D8196","#7D99AA")) +
  
  labs(title="Bar Chart for the Major Email Categories",
     subtitle= "Comparing the daily emails received in different categories",
     caption = "Souce: Email Observation Form",
     x= "Email Categories",
     y="Number of Emails")


```

<br>

```{r}

ggplot(data = latest_data) +
  geom_bar(aes(x = more_email_address), fill =c (
    "#CCFF00","#191970" )) +
  
  labs(title="Bar Chart for Two Email Addresses Comparison",
     subtitle= "Comparison of the number of daily emails received in two different email addresses",
     caption = "Souce: Email Observation Form",
     x= "Email Addresses",
     y="Number of Emails")

```

<br>

```{r}
latest_data %>%
  ggplot() +
  geom_bar(aes(y= more_email_address, fill= major_emails)) +
  scale_fill_manual(values= c (
   "#FA994A", "#B7410E","#FFCE1B","#069494","#194454"
  )) +
  
  labs(title="Bar Chart Showing Email Categories for Two Accounts",
       subtitle= "Comparing the daily number of emails received in two email addresses, \nconsidering the categories of the emails",
       caption = "Souce: Email Observation Form",
       x= "Number of Emails",
       y="Email Addresses")

```


